A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-09-17 paper/main.tex
mention validation analysis in abstract

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten
verbraucht} \thispagestyle{fancy} \begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest
Gump'' and its audio-description (i.e. the audio-only variant of the movie) as
an addition to a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
information about the exact timing of each of the more than 2500 spoken
sentences, 16000 words (including 202 non-speech vocalizations), 66000 phonemes,
and their corresponding speaker. Additionally for every word, we provide
lemmatization, a simple part-of-speech-tagging (15 grammatical categories), a
detailed part-of-speech tagging (43 grammatical categories), syntactic
dependencies, and a semantic analysis based on word embeddings which represents
each word in a 300-dimensional semantic space. This annotation enables
researchers to create sophisticated models of brain activity related to
phonetics, grammar, syntax, and semantics under conditions of real-life
complexity.  \end{abstract}

\section*{Keywords}
% maximal 8
annotation, language, speech, narrative, natural stimulation, fMRI, studyforrest

@@

\todo[inline]{``Dataset content'' vs. ``Data and software availability''}

@@

% data-driven methods..
Data-driven methods like inter-subject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data circumventing this bottleneck.
% ..are nice but:
However, data-driven methods alone fall usually short of pinpointing their
results to specific stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), that are based on
stimulus annotations can be useful to test hypotheses on specific brain
functions under more ecologically valid conditions, to statistically control
confounding stimulus features, and to explain not just ``how'' the brain is
responding to a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
Studies using GLMs based on annotations of a stimulus' temporal structure have
elucidated for example how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2020language}.
% combination of data-driven and model-driven approaches
Furthermore, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

@@

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability. ~170 words => das wird beim folgenden Schreiben
% definitiv nichts werden intro
In order to assess the annotation's quality, we investigated if contrasting
speech-related events to events without speech lead to increased activation in
areas known to be involved in language processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if two similar linguistic concepts (proper nouns and nouns)
providing high semantic information contrasted with a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.

@@

% Discussion words > no-speech
For the contrast words > no-speech, results show increased hemodynamic activity
in a bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
These clusters resemble results of previous studies that implemented an ISC
approach to analyze fMRI data of naturalistic auditory stimuli
\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
% differences
We don't find significantly increased activations in midline areas (like the
posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
frontal cortex) which showed synchronized activity across subjects in previous
studies.
% Wilson (2008): ISC + GLM
In this regard, our results are similar to \citep{wilson2008beyond} who
implemented both an ISC and a GLM analysis. In this study, the ISC analysis
showed synchronized activity in midline areas but the GLM analysis contrasting
blocks of listening to narratives to blocks of a resting condition showed
significantly decreased activity in these areas.
\todo[inline]{our reverse contrast (no-speech > words): clusters in posterior \&
anterior cingulate (and subcallosal c. \& insulae bilaterally); I think opening
the pandora's box of the reverse contrasts is not worth it here}

@@

\section*{Data availability}
\todo{cf. other F1000 papers but probably a gift for the master}
\texttt{This section will be auto-generated.}

@@

\todo[inline]{the paper needs to serve a purpose:
    a) documentation for the annotation.
    b) attract people to use this work for their own studies.
    I would even argue that this is the \textit{main} purpose, given that the
    annotation in itself represents to scientific progress. The need to give an
    accurate assessment what this can be used for and what is problematic or
    impossible.  ATM this is the only statement in this regard: 'facilitates
    modeling of hemodynamic brain responses correlating with speech-related
events' and the only indication of purpose is 'additional confound measures'. I
thin this is incongruent with the amount of work and the level of detail of
this annotation; CH: let's discuss that personally}

\section*{Conclusions}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enables independent
working groups to create sophisticated models of hemodynamic activity
correlating with linguistics aspects like phonetics, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our analysis that we ran to assess the dataset's quality shows that the annotation's content can indeed be used to isolate speech-related networks in the human brain under life-like conditions.

>>>>

\thispagestyle{fancy}

\begin{abstract}
% up to 300 words intro
Here we present an annotation of speech spoken in the audio-visual movie
``Forrest Gump'' and its audio-description (i.e. the audio-only variant of the
movie) as an addition to a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}).
% anno content 1
The annotation provides information about the exact timing of each of the more
than 2500 spoken sentences, 16000 words (including 202 non-speech
vocalizations), 66000 phonemes, and their corresponding speaker.
% anno content 2
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging (15 grammatical categories), a detailed part-of-speech
tagging (43 grammatical categories), syntactic dependencies, and a semantic
analysis based on word embedding which represents each word in a
300-dimensional semantic space.
% validation
To validate the dataset's quality, we build a model of hemodynamic brain
activity based on information drawn from the annotation.
% why bother
Results suggest that the annotation's content and quality enable independent
researchers to create sophisticated models of brain activity correlating with a
variety of linguistic aspects under conditions of real-life complexity.
\end{abstract} \todo{validation is now (carefully) mentioned; 150 of 300 words
used for abstract}

\section*{Keywords}
% maximal 8
annotation, language, speech, narrative, naturalistic stimulus, fMRI, studyforrest

@@

@@

% data-driven methods..
Data-driven methods like inter-subject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data circumventing this bottleneck.
% ..are nice but:
However, data-driven methods alone fall usually short of pinpointing their
results to specific stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), that are based on
stimulus annotations can be useful to test hypotheses on specific brain
functions under more ecologically valid conditions, to statistically control
confounding stimulus features, and to explain not just ``how'' the brain is
responding to a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
Studies using GLMs based on annotations of a stimulus' temporal structure have
elucidated for example how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2020language}.
% combination of data-driven and model-driven approaches
Furthermore, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve the interpretability of results \citep{lahnakoski2012stimulus}.

@@

\section*{Dataset validation}
\todo[inline]{``Information about any validation carried out and/or any
    limitations of the datasets, including any allowances made for controlling
bias or unwanted sources of variability. ~170 words'' 170 words? lol}
% intro
In order to assess the annotation's quality, we investigated if contrasting
speech-related events to events without speech lead to increased activation in
areas known to be involved in language processing \citep{hickok2007cortical}.
% nouns and proper nouns resp. > coordinate junctions
Moreover, we tested if two similar linguistic concepts (proper nouns and nouns)
providing high semantic information contrasted with a concept providing low
semantic information (coordinate conjunctions) lead to increased activation in
congruent brain areas.

@@

% Discussion words > no-speech
For the contrast words > no-speech, results show increased hemodynamic activity
in a bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
These clusters resemble results of previous studies that implemented an ISC
approach to analyze fMRI data of naturalistic auditory stimuli
\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
% differences
We do not find significantly increased activations in midline areas (like the
posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
frontal cortex) which showed synchronized activity across subjects in previous
studies.
% Wilson (2008): ISC + GLM
In this regard, our results are similar to \citep{wilson2008beyond} who
implemented both an ISC and a GLM analysis. In this study, the ISC analysis
showed synchronized activity in midline areas but the GLM analysis contrasting
blocks of listening to narratives to blocks of a resting condition showed
significantly decreased activity in these areas.
\todo[inline]{our reverse contrast (no-speech > words): clusters in posterior \&
anterior cingulate (and subcallosal c. \& insulae bilaterally); I think opening
the pandora's box of the reverse contrasts is not worth it here}

@@

\section*{Data availability} \todo[inline]{``This section will be
auto-generated.'' What do we have to do here? I cleaned input datasets
(speechanno and speechanno as subdataset in validation analysis) of this paper
repo from the descriptive nouns}

@@

\section*{Conclusions}
\todo[inline]{give an accurate assessment what this can be used for and what is
    problematic or impossible.  ATM this is the only statement in this regard:
    'facilitates modeling of hemodynamic brain responses correlating with
    speech-related events' and the only indication of purpose is 'additional
confound measures'. I thin this is incongruent with the amount of work and the
level of detail of this annotation; CH: let's discuss that personally}
% what the paper is about
As an extension of the studyforrest dataset, we present an annotation of spoken
language in the two hours lasting ``research cut'' of the audio-visual movie
``Forrest Gump'' and its temporally aligned audio-description.
% what we did
We annotated the onset and offset of sentences, words and phonemes, and the
corresponding speaker's identity.
% what for
An additional tagging of each word's linguistic features enables independent
working groups to create sophisticated models of hemodynamic activity
correlating with linguistics aspects like phonetics, grammar, syntax, and
semantics occurring in two naturalistic stimuli.
% results
Results of our analysis that we ran to assess the dataset's quality shows that
the annotation's content can indeed be used to isolate speech-related networks
in the human brain under life-like conditions.
